---
title: "RMarkdown_and_Leaflet"
author: "Joao Felizardo"
date: "5/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

In this document I'm going to ducument Portugal main cities using [worlcities](https://www.kaggle.com/max-mind/world-cities-database) dataset, containing the latitude and longitude of each city. I'll use `Leaflet` R library to build maps with information about the cities.

#### Preparing environment
```{r echo=FALSE}
library(leaflet)
```

#### Reading and cleaning the dataset
```{r}
# Reading .csv file
wordcities <- read.csv("worldcities.csv")
# Extracting info only related to Portugal
portugal <- wordcities[wordcities$country == "Portugal",]
# Droping not needed columns for this case
drop <- c('city_ascii', 'country', 'iso2', 'iso3', 'id')
pt <- portugal[,!(names(portugal) %in% drop)]
head(pt)
```

#### Building the map
```{r warning=FALSE}
pt_map <- pt %>%
  leaflet() %>% 
  addTiles() %>%
  addMarkers()
pt_map
```

#### Adding icon to the map
```{r}
# Adding Lisbon icon 
ptIcon <- makeIcon(
  iconUrl = ifelse(pt$city == "Lisbon",
                     "http://media.gettyimages.com/vectors/travel-lisbon-icon-vector-id641409438?s=170667a&w=1007",
                   "https://cdn.countryflags.com/thumbs/portugal/flag-round-500.png"),
  iconWidth = 31, iconHeight = 31,
  iconAnchorX = 31, iconAnchorY = 16
)

pt_map <- pt %>%
  leaflet() %>% 
  addTiles() %>%
  addMarkers(icon = ptIcon)
pt_map
```


#### Adding popup with the population number to the map
```{r}
pt_map <- pt %>%
  leaflet() %>%
  addTiles() %>%
  addMarkers(icon = ptIcon, popup = as.character(pt$population)) %>%
  addCircles(weight = 1, radius = sqrt(pt$population) * 30)
pt_map
```

The popup on the cities icon's is the number of inhabitants of the each district.
